DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-07-01 ase2017/paper.tex
reviewed results
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

>>>>

For our experiments, we observed that the \tool finds at least one controller synthesized 
for our set of benchmarks represented by transfer function or state-space equations.

We employed a diverse set of real-world benchmarks extracted from the literature. 
However, this set of benchmarks is still limited within the scope of this paper, and 
the performance may not be generalized to other benchmarks. The media runtime 
for our benchmarks is $124$\,s, and the average synthesis time amounts $35.5$\,s 
for state-space benchmarks, while for transfer function benchmarks, the average is $123.6$\,s.

In particular, we can reproduce the stability property in the synthesized controller 
for a DC motor plant described in Eq.~\eqref{tf-synth-controller}, simulating the step response 
in MATLAB. As can be seen, Fig.~\ref{tf-step-response} shows that the synthesized controller 
using the \tool is stable, giving the reliability about the results of our tool.

\begin{equation}
\label{tf-synth-controller}
C(z)=\frac{-0.3466796875z+0.015625}{-0.5z^{2}+0.19921875z}.
\end{equation}

\begin{figure}[ht]
  \includegraphics[width=0.5\textwidth]{tf-step-response.eps}
  \caption{Step response for the Eq.~\eqref{tf-synth-controller} describing a stable system for the DC motor plant.}
  \label{tf-step-response}
\end{figure}

Regarding the state-space representation, we can check in the plant expressed by 
Eq.~\eqref{ss-synth-controller} (that describes a system for pendulum) that the feedback matrix 
(represented by Eq.~\eqref{ss-synth-feedback}) generated by \tool, when combined with the plant 
with the state equations described in Eq.~\eqref{ss-synth-controller} is also stable, as can been seen in Fig.~\ref{ss-step-response}.
%
\begin{equation}
\label{ss-synth-controller}
\begin{split}
x(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\
\end{equation}

Where,
%
$$A = \left[\begin{array}{cc}-1.999909737361046&-1.000000000000000\\1&0\end{array}\right],$$
$$B = \left [\begin{array}{c}4\\0\end{array}\right],$$
$$C = \left [\begin{array}{cc}-1.756887232846049&-1.7494556607764090\end{array}\right],$$
$$\quad D = \left [\begin{array}{c}9.8\end{array}\right].$$

\begin{equation}
\label{ss-synth-feedback}
\begin{split}
K &= \left [\begin{array}{cc}-0.5898&-0.1914\end{array}\right]
\end{split}\
\end{equation}

\begin{figure}[ht]
  \includegraphics[width=0.5\textwidth]{ss-step-response.eps}
  \caption{Step response for the Eq.~\eqref{ss-synth-controller} describing a stable system for the pendulum plant.}
  \label{ss-step-response}
\end{figure}

The synthesized controllers are validated to be stable using the MATLAB approach, 
which means that our results are reliable for control engineers. A link to the full experimental environment, 
including the scripts to reproduce the results, all benchmarks and the tool, is provided online in our website\footnote{\url{www.dsverifier.org}}.
